ISSSV1337 Group 5 Report

### 2022-08-03 Report/Group 5 report v2.Rmd
Centred image.

```{r, echo=FALSE, out.width="50%", fig.cap="The Norwegian Cancer Society started posting financial statement PDFs on their website in 2019."}
# Illustration only published for some years example
knitr::include_graphics("Images/Kreftforeningen_starts2019.png")
```

@@

- **Private/public proportion**:
  - Calculates the percentage of non-commercial or activity-based income that is derived from private contributions and membership fees as opposed to public grants:

>>>>

```{r, echo=FALSE, out.width="50%", fig.align='center', fig.cap="The Norwegian Cancer Society started posting financial statement PDFs on their website in 2019."}
# Illustration only published for some years example
knitr::include_graphics("Images/Kreftforeningen_starts2019.png")
```

@@

\newpage
- **Private/public proportion**:
  - Calculates the percentage of non-commercial or activity-based income that is derived from private contributions and membership fees as opposed to public grants:
